Plots_GAM

### 2024-06-09 Code/Plots_GAM.Rmd
Regenerated .tiff

#"..", takes up a level in the directory path
DataIn <- file.path("..","Data", "CleanData")
DataOut <- file.path("..","Data", "CleanData")
PlotsIn <- file.path("..","Output", "Figures")
PlotsOut <- file.path("..","Output", "Figures")
PlotsOutPLOS <- file.path("..", "OutPut", "PLOSFiguresRound1")

@@

# MED4PARGAM is Fig4.tiff for PLOSONE submission
 ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = MED4PARGAM, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")

@@

# SS120PARGAM is Fig6.tiff for PLOSONE submission
 ggsave(file = file.path(PlotsOutPLOS, "Fig6.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")

@@

# MIT9313PARGAM is Fig8.tiff for PLOSONE submission
 ggsave(file = file.path(PlotsOutPLOS, "Fig8.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10,  compression = "lzw")

>>>>

#"..", takes up a level in the directory path
DataIn <- file.path("..","Data", "CleanData")
DataOut <- file.path("..","Data", "CleanData")
PlotsIn <- file.path("..","Output", "Figures")
PlotsOut <- file.path("..","Output", "Figures")
PlotsOutPLOS <- file.path("..", "OutPut", "PLOSRound2")

@@

# MED4PARGAM is Fig3.tiff for PLOSONE submission
 ggsave(file = file.path(PlotsOutPLOS, "Fig3.tiff", fsep = .Platform$file.sep), plot = MED4PARGAM, device = NULL, scale = 1,  height = 16, width = 12, compression = "lzw")

@@

# SS120PARGAM is Fig4.tiff for PLOSONE submission
 ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = SS120PARGAM, device = NULL, scale = 1,  height = 16, width = 12, compression = "lzw")

@@

# MIT9313PARGAM is Fig5.tiff for PLOSONE submission
 ggsave(file = file.path(PlotsOutPLOS, "Fig5.tiff", fsep = .Platform$file.sep), plot = MIT9313PARGAM, device = NULL, scale = 1,  height = 18, width = 12,  compression = "lzw")
